---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparseVector

<!-- badges: start -->
[![R-CMD-check.yaml](https://github.com/vramdas06/sparseVectorClass/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/vramdas06/sparseVectorClass/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of sparseVector is to define an S4 class that represents sparse numeric vectors. The methods in this package perform much more efficiently than typical dense vector operations when the vector contains a lot of 0s. This package includes coersion methods between sparse and dense vectors, simple arithmetic operations on sparse vectors, and more advanced capabilities like plotting sparse vector overlap and computing the mean, norm, and the standardized vector. 

## Installation

You can install the development version of sparseVector like so:

``` r
devtools::install_github("vramdas06/sparseVectorClass")
```

## Example

This is a basic example which shows you how to use sparseVector:

```{r example}
library(sparseVector)
x <- c(1, 0, 3, 0, 5, 0, 0)
sparse_x <- as(x, "sparse_numeric")
sparse_x

x <- as(c(1, 0, 3, 0, 5), "sparse_numeric")
y <- as(c(0, 2, 3, 0, 1), "sparse_numeric")

# Add two sparse vectors
x + y

# Subtract
x - y

# Multiply (element-wise)
x * y

# Plot
plot(x, y)

```
