---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparseVector

<!-- badges: start -->
[![R-CMD-check.yaml](https://github.com/vramdas06/sparseVectorClass/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/vramdas06/sparseVectorClass/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

sparseVector implements an S4 class for sparse numeric vectors, vectors where most elements are zeros. By storing only non-zero values and their positions, operations are much faster than regular dense vectors. The package provides methods for converting between sparse and dense formats, arithmetic operations (addition, subtraction, multiplication), and computing mean, norm, and standardized vectors. You can also visualize overlapping non-zero elements between vectors using sparseVector.

## Installation

You can install the development version of sparseVector like so:

``` r
devtools::install_github("vramdas06/sparseVectorClass")
```

## Example

This is a basic example which shows you how to use sparseVector:

```{r example}
library(sparseVector)
x <- c(1, 0, 3, 0, 5, 0, 0)
sparse_x <- as(x, "sparse_numeric")
sparse_x

x <- as(c(1, 0, 3, 0, 5), "sparse_numeric")
y <- as(c(0, 2, 3, 0, 1), "sparse_numeric")

# Add two sparse vectors
x + y

# Subtract
x - y

# Multiply (element-wise)
x * y

# Plot
plot(x, y)

```
